Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-01-22 Paper/paper.tex
New block diagram, starting to work on robustness experiments

% Template for ICIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,amssymb,amsfonts,amsthm,graphicx}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{1DExample.pdf}
\caption{An illustration of our technique on a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).  We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.  From this, we use the mean of the birth and death time of the largest persistence dot (row 2, column 2) to autotune the spatial bandwidth for the graph Laplacian (upper right two figures for the weighted and unweighted Laplacian), from which we derive a map to the circle (middle, right two plots).  From this, we derive circular coordinates, which we can use to do a simple reordering (row 3 column 2) or median consensus (row 3, column 3), using interpolated votes from all windows interleaved by the coordinates (row 3, column 2). }
\label{fig:ConceptFigure}
\end{figure}

@@

\begin{algorithm}[t]
  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
  \begin{algorithmic}[1]
    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times N}$
    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$
    \If {median}
        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
    \Else
        \State Order first frames in each window by $\theta$
    \EndIf
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{Laplacian Circular Coordinates}
    \begin{algorithmic}[1]
    \Procedure{CircCoords}{$X$, $L$}
    \State $\hat{X} \gets $ image pyramid level $L$ of $X$
    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times N}$
    \State $y \gets$ 1D ISOMAP($Y$) \cite{tenenbaum2000global}
    \State $d \gets$ fundamental period estimate of $y$ \cite{Mcleod05asmarter}
    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$

    \State $I \gets dgm_1[Z] = ((b_1, d_1), ... (b_k, d_k))$
    \State $i \gets \argmax_{i}[d_i - b_i]$, $\sigma \gets b_i + \frac{1}{2}(d_i - b_i)$
    \State $d_{ij} \gets ||Z_i - Z_j||_2$
    \If {weighted}
        \State $A_{ij} \gets e^{-d_{ij}^2/\sigma}$
    \Else
        \State $A_{ij} \gets \left\{ \begin{array}{cc} 1 & d_{ij} \leq \sigma \\ 0 & \text{otherwise} \end{array} \right\}$
    \EndIf
    \State $A_{ii} \gets 0, D_{ii} \gets \sum_{j=1}^M A_{ij}, D_{i, j \neq i} \gets 0$, $L \gets D - A$
    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zcs
    \State $\theta \gets \cos^{-1}(v_2/v_1)$\\
    \Return ($\theta$, d)
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

>>>>

% Template for ICIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,amssymb,amsfonts,amsthm,graphicx}

@@

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{BlockDiagram.pdf}
\caption{An block diagram of our technique, illustrated by a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).  We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.  From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\sigma$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
\label{fig:ConceptFigure}
\end{figure*}
